We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-01-22 paper/paper.tex
editing conclusions

In this paper we develop and demostrate a method to quantify the
asphericity of the satellite distribution in the Local Group.
The method uses as a basic condition the spherical randomization of
satellite positions (observed or simulated). 
The scalars describing the satellite distribution in each galaxy are
then normalized to the mean value and standard deviation in the
randomized samples. 
In observations we limit our analysis to the 11 brightest satellites 
in the Milky Way and Andromeda. 
For numerical data we use the Illustris-1 and the ELVIS simulations.

>>>>

In this paper we develop and demostrate a method to quantify the
asphericity of the satellite distribution in the Local Group.
The method uses as a reference point the spherically randomized data
of the system under study.
We first measure the width and axis ratios for the satellite
distribution of interest. Then, we measure the same quantities for the spherical
randomizations, to finally renormalize the initial results to the mean
value and standard deviation from the randomized samples.

We do not look for planes  or coherent kinematical structures in the
interest of keeping our study simple and robust.
In observations we limit our analysis to the 11 brightest satellites 
in the Milky Way and Andromeda. 
For numerical data we use the Illustris-1, Illustris-1-DM and the
ELVIS simulations.
